---
title: "Plots for Murray"
author: "Jackie Ouzman"
date: "17/11/2023"
output: html_document
---

```{r setup, include=FALSE}

library(ggplot2)
library(readxl)
library(tidyverse)
#library(multcompView)

library(plotly)

library(tidyverse)
library(hrbrthemes)
library(viridis)
library(forcats)
library(hrbrthemes)
library(stringr)
#install.packages("hrbrthemes")

library(ggpubr)


```

Murray would like the data to be summaries before any plots are created.
The plots created in August and for all other work is all the data rather than any average.

```{r Get the data, include=FALSE}

#Bring in the data#

data_file_control <- "X:/Therese_Jackie/Sandy_soils/Development_database/completeDB/sites_control_merged.csv"



summary_control_data_all <- read_csv(data_file_control, 
                                     col_types = cols(rep_block = col_character()))

########################################################################################################################################

##label problem with Mt Damper
summary_control_data_all <- summary_control_data_all %>% 
  mutate(
    site_sub = case_when(
      site_sub == "Mt Damper" ~ "Mt_Damper",
      TRUE ~ site_sub))

##label problem with Ouyen
summary_control_data_all <- summary_control_data_all %>% 
  mutate(
    site_sub = case_when(
      site_sub == "Oyen_Spade" ~ "Ouyen_Spade",
      TRUE ~ site_sub))
summary_control_data_all <- summary_control_data_all %>% 
  mutate(
    site = case_when(
      site == "Oyen_Spade" ~ "Ouyen_Spade",
      TRUE ~ site))

```



Some sites are excluded from analysis - based on review by Mel and Therese.
This list has been reviewed by Therese in Nov 2023, and is unchanged from August work.


```{r Get the data filter removed data, include=FALSE}

summary_control_data_all <- summary_control_data_all %>% 
  filter(site_display != "remove")

```







  
```{r working out how many modification all 1, message=FALSE, warning=FALSE, include=FALSE}
#####################################################################################
#####  soil modifications      #####
#####################################################################################

### get the soil modification from the Descriptors

#1 soil modification with depth
summary_control_data_all <- summary_control_data_all %>% 
  mutate(soil_modification_depth =  str_extract(summary_control_data_all$Descriptors, "[^_]+"))#keep everything before the first_


#1.1 Youndhusband has 'Unmodified+DeepTill.18' which needs to be recoded as "Unmodified"

summary_control_data_all <- summary_control_data_all %>% 
  mutate(soil_modification_depth = case_when(
    soil_modification_depth == "Unmodified+DeepTill.18" ~ "Unmodified",
    TRUE ~ soil_modification_depth))

#how many modification_depth
soil_modification_depth <- summary_control_data_all %>% 
  distinct(soil_modification_depth) %>% 
  arrange(soil_modification_depth) %>% 
  filter(soil_modification_depth != "Unmodified")

count(soil_modification_depth) #20 excluding the unmodified


#1a working clms - soil modification without depth 1 only
summary_control_data_all <- summary_control_data_all %>% 
  mutate(soil_modification_1 =  str_extract(summary_control_data_all$Descriptors, "[^.]+"))#keep everything before the first .

#the Unmodified seems to have a problem this fixes it :)
summary_control_data_all <- summary_control_data_all %>% 
  mutate(soil_modification_1 = str_extract(summary_control_data_all$soil_modification_1, "[^_]+")) #keep everything after the first _

#1a.1 Youndhusband has 'Unmodified+DeepTill.18' which needs to be recoded as "Unmodified"

summary_control_data_all <- summary_control_data_all %>% 
  mutate(soil_modification_1 = case_when(
    soil_modification_1 == "Unmodified+DeepTill" ~ "Unmodified",
    TRUE ~ soil_modification_1))

summary_control_data_all %>%  distinct(soil_modification_1) %>% arrange(soil_modification_1)





#1a working clms - 2 soil modification without depth 2

#temp <- summary_control_data_all %>%  distinct(soil_modification_depth) %>% arrange(soil_modification_depth)

summary_control_data_all <- summary_control_data_all %>% 
  mutate(soil_modification_2 = case_when(
    soil_modification_depth == "Rip.50Spade.30" ~        "Rip+Spade",
    soil_modification_depth == "Rip.60Spade.30" ~        "Rip+Spade",
    soil_modification_depth == "Rip.45IncRip+Spade.30" ~ "IncRip+Spade",
    soil_modification_depth == "Rip.60IncRip+Spade.30" ~ "IncRip+Spade",
    
    soil_modification_depth == "Rip.30IncRip" ~           "IncRip",
    soil_modification_depth == "Rip.40IncRip" ~           "IncRip",
    soil_modification_depth == "Rip.45IncRip" ~           "IncRip",
    soil_modification_depth == "Rip.50IncRip" ~           "IncRip",
    soil_modification_depth == "Rip.60IncRip" ~           "IncRip",
    
    soil_modification_depth == "Pre" ~           "Unmodified",
    
    
    TRUE ~ "NA"
  ))



summary_control_data_all %>%  distinct(soil_modification_2) %>% arrange(soil_modification_2)


#2 all soil modification without depth (if 2 soil modification used keep this)	

summary_control_data_all <- summary_control_data_all %>% 
  mutate(soil_modification = case_when(
    soil_modification_2 == "NA" ~ soil_modification_1,
    TRUE ~ soil_modification_2
  ))


summary_control_data_all %>%  distinct(soil_modification) %>% arrange(soil_modification)

### remove the working clms
summary_control_data_all <- summary_control_data_all %>% 
  dplyr::select(-soil_modification_1,
                -soil_modification_2)


#how many modification without depth
soil_modification_depth <- summary_control_data_all %>% 
  distinct(soil_modification) %>% 
  arrange(soil_modification) %>% 
  filter(soil_modification != "Unmodified")

count(soil_modification_depth) #8 excluding the unmodified 



#####################################################################################
#####  soil amendments      #####
#####################################################################################



### get the soil Amendment from the Descriptors
# gets all the amendments
summary_control_data_all <- summary_control_data_all %>%
  mutate(amendment_all = sub("^[^_]*_", "", summary_control_data_all$Descriptors)) #keep everything after the first _
#pull out the first amendment listed but has rates
summary_control_data_all <- summary_control_data_all %>%
  mutate(amendment_1 = str_extract(summary_control_data_all$amendment_all, "[^.]+"))#keep everything before the first
#removed the rates in the first amendment listed
summary_control_data_all <- summary_control_data_all %>%
  mutate(amendment_1 = str_extract(summary_control_data_all$amendment_1, "[^@]+")) #keep everything before the first @

temp <- summary_control_data_all %>%  distinct(amendment_1) %>% arrange(amendment_1)


summary_control_data_all <- summary_control_data_all %>% 
  mutate(amendment_2 = case_when(
    
    amendment_all ==  "30+30_Fert.banded_30" ~        "Fert",
    amendment_all ==  "30+30_Fert.banded_30_annual" ~ "Fert",
    amendment_all ==  "30+30_none" ~                  "none",
    amendment_all ==  "30+30_none_annual" ~           "none",
    amendment_all ==  "30+7.5_none" ~                  "none",
    amendment_all ==  "30+7.5_none_annual" ~           "none",
    amendment_all ==  "Cl.incorp_30.Gypsum.incorp_30" ~ "Cl+Gypsum",
    amendment_all ==  "Cl@20.incorp_20.Clay.incorp_20" ~ "Cl+Clay",
    amendment_all ==  "Cl@20.incorp_20.Fert.surface" ~ "Cl+Fert",
    amendment_all ==  "Cl@20.incorp_20.Fert.surface.Clay.incorp_20" ~ "Cl+Fert+Clay",
    amendment_all ==  "Cl@20.incorp_8.Clay.incorp_8" ~ "Cl+Clay",
    amendment_all ==  "Cl@20.incorp_8.Fert.surface" ~ "Cl+Fert",
    amendment_all ==  "Cl@20.incorp_8.Fert.surface.Clay.incorp_8" ~ "Cl+Fert+Clay",
    amendment_all ==  "Cl@3.incorp_30.Lime.incorp_8" ~ "Cl+Lime",
    amendment_all ==  "Cl@5.incorp_20.Clay.incorp_20" ~ "Cl+Clay",
    amendment_all ==  "Cl@5.incorp_20.Fert.surface" ~ "Cl+Fert",
    amendment_all ==  "Cl@5.incorp_20.Fert.surface.Clay.incorp_20" ~ "Cl+Fert+Clay",
    amendment_all ==  "Cl@5.incorp_8.Clay.incorp_8" ~ "Cl+Clay",
    amendment_all ==  "Cl@5.incorp_8.Fert.surface" ~ "Cl+Fert",
    amendment_all ==  "Cl@5.incorp_8.Fert.surface.Clay.incorp_8" ~ "Cl+Fert+Clay",
    amendment_all ==  "drill_20+20_Fert.banded_20" ~ "Fert",
    amendment_all ==  "drill_20+20_Fert.banded_20_annual" ~ "Fert",
    amendment_all ==  "drill_20+20_none" ~ "none",
    amendment_all ==  "drill_20+20_none_annual" ~ "none",
    amendment_all ==  "drill_20+7.5_none" ~ "none",
    amendment_all ==  "drill_20+7.5_none_annual" ~ "none",
    amendment_all ==  "Fert.band_30.Clay.incorp_10" ~ "Fert+Clay",
    amendment_all ==  "Fert.incorp_30.Clay.incorp_30" ~ "Fert+Clay",
    amendment_all ==  "Fert.incorp_30.K_added.incorp_30" ~ "Fert+K",
    amendment_all ==  "Fert.surface.Clay.incorp_20" ~ "Fert+Clay",
    amendment_all ==  "Fert.surface.Clay.incorp_8" ~ "Fert+Clay",
    amendment_all ==  "Fert_APP.band_45" ~ "Fert",
    amendment_all ==  "Fert_High.band_45" ~ "Fert",
    amendment_all ==  "Fert_Low.band_45" ~ "Fert",
    amendment_all ==  "K_added.surface" ~ "K",
    amendment_all ==  "Lc.incorp_30.Clay.incorp_30" ~ "Lc+Clay",
    amendment_all ==  "Lc.incorp_30.Fert.incorp_30.Clay.incorp_30" ~ "Lc+Fert+Clay",
    amendment_all ==  "Lc@1.incorp_30.K_added.surface" ~ "Lc+K",
    amendment_all ==  "Lc@10.incorp_30.K_added.surface" ~ "Lc+K",
    amendment_all ==  "Lc@15.incorp_30.K_added.surface" ~ "Lc+K",
    amendment_all ==  "Lc@2.incorp_30.K_added.surface" ~ "Lc+K",
    amendment_all ==  "Lc@20.incorp_30.K_added.surface" ~ "Lc+K",
    amendment_all ==  "Lc@4.incorp_30.K_added.surface" ~ "Lc+K",
    amendment_all ==  "Lc@6.incorp_30.K_added.surface" ~ "Lc+K",
    amendment_all ==  "Lc@8.incorp_30.K_added.surface" ~ "Lc+K",
    amendment_all ==  "Vet_Cer_In.incorp_30" ~ "Vetch_Cer",
    
    
    TRUE ~ amendment_1
  ))

unique(summary_control_data_all$amendment_2)

summary_control_data_all <-  summary_control_data_all %>% 
  mutate(amendment_123 = amendment_2)


#tidy up working outs
summary_control_data_all <- summary_control_data_all %>%
  dplyr::select(-amendment_all, -amendment_1, -amendment_2)
names(summary_control_data_all)


################################################################################


```






Add code for amendments classed as

- animal

- plant

- non organic

- none

- mixed

```{r code for amendment plant and animals, message=FALSE, warning=FALSE, include=FALSE}

summary_control_data_all<- summary_control_data_all %>% 
  mutate(amendment_code1 = case_when(
    amendment_123 ==  "none" ~ "none",
    
    amendment_123 == "drill_20+7"              ~ "none",
    amendment_123 == "30+30_none_annual"       ~ "none",
    amendment_123 == "drill_20+20_none"        ~ "none",
    amendment_123 == "drill_20+20_none_annual" ~ "none",
    amendment_123 == "30+7"                    ~ "none",
    amendment_123 == "30+30_none"              ~ "none",
    
    
    amendment_123 ==  "Cl" ~ "animal",
    
    amendment_123 ==  "Lc" ~ "plant",
    amendment_123 ==  "Cereal" ~ "plant",
    amendment_123 ==  "Vetch" ~ "plant",
    amendment_123 ==  "Vet_Cer" ~ "plant",
    amendment_123 ==  "Vetch_Cer" ~ "plant",
    amendment_123 ==  "Vet_Cer_In" ~ "plant", 
    amendment_123 ==  "Com" ~ "plant",
    
    
    amendment_123 ==  "Fert" ~        "fertiliser",
    amendment_123 ==  "Fert_High"   ~ "fertiliser",
    amendment_123 ==  "Fert_Low"    ~ "fertiliser",
    amendment_123 ==  "Fert_APP"    ~ "fertiliser",
    amendment_123 ==  "K_added"     ~ "fertiliser",
    amendment_123 ==  "K"     ~ "fertiliser",
    amendment_123 ==  "FertK_added" ~ "fertiliser",
    amendment_123 ==  "Fert+K" ~ "fertiliser",
    
    amendment_123 ==  "30+30_Fert"  ~ "fertiliser",
    amendment_123 ==  "drill_20+20_Fert" ~ "fertiliser",
    
    amendment_123 ==  "Gypsum" ~ "non organic",
    amendment_123 ==  "Clay" ~ "non organic",
    amendment_123 ==  "Lime" ~ "non organic",
    amendment_123 ==  "Bi_Agra" ~ "non organic",
    amendment_123 ==  "SE14" ~ "non organic",
    
    
    amendment_123 ==  "ClFertClay" ~ "mixed",
    amendment_123 ==  "Cl+Fert+Clay" ~ "mixed",
    amendment_123 ==  "ClFert" ~ "mixed",
    amendment_123 ==  "Cl+Fert" ~ "mixed",
    amendment_123 ==  "ClClay" ~ "mixed",
    amendment_123 ==  "Cl+Clay" ~ "mixed",
    
    amendment_123 ==  "ClLime" ~ "mixed",
    amendment_123 ==  "Cl+Lime" ~ "mixed",
    amendment_123 ==  "ClGypsum" ~ "mixed",
    amendment_123 ==  "Cl+Gypsum" ~ "mixed",
    
    amendment_123 ==  "LcFert" ~ "mixed",
    amendment_123 ==  "Lc+Fert" ~ "mixed",
    amendment_123 ==  "LcClay" ~ "mixed",
    amendment_123 ==  "Lc+Clay" ~ "mixed",
    amendment_123 ==  "LcFertClay" ~ "mixed",
    amendment_123 ==  "Lc+Fert+Clay" ~ "mixed",
    amendment_123 ==  "LcK_added" ~ "mixed",
    amendment_123 ==  "Lc+K" ~ "mixed",
    
    amendment_123 ==  "FertClay" ~ "mixed",
    amendment_123 ==  "Fert+Clay" ~ "mixed",
    
    
    TRUE ~ "check"
    
    
  ))
```



```{r output working, echo=FALSE, message=FALSE, warning=FALSE}

write.csv(summary_control_data_all, "X:/Therese_Jackie/Sandy_soils/for_Murray/paper_Oct_2023/workings/summary_control_data_am_code_selected_sites_step1.csv")

```


## Scatter Plots control vs treatments yields **with amendment groupings**

```{r average site, year and treatment, echo=FALSE, message=FALSE, warning=FALSE}
##select clms

select_control_data_all <- summary_control_data_all %>% 
  select(site,year, Descriptors,
         yield, control_yield,
         soil_modification,
         amendment_code1)

### average yield and control yield

ave_site_yr_treat <- select_control_data_all %>% 
  group_by(site,year, Descriptors, soil_modification , amendment_code1) %>% 
  summarise(yield_av = mean(yield, na.rm=TRUE),
           control_yld_av = mean(control_yield, na.rm=TRUE)
            )
#head(ave_site_yr_treat)
ungroup(ave_site_yr_treat)

```



```{r scatter amendment, echo=FALSE, message=FALSE, warning=FALSE}


ave_site_yr_treat$amendment_code1 <-
  factor(ave_site_yr_treat$amendment_code1,
         #levels = c("animal", "plant", "fertiliser"))
         levels = c("animal", "plant", "fertiliser","non organic", "mixed"))


ave_site_yr_treat %>%  
  filter(amendment_code1 != "none") %>%  
  filter(amendment_code1 != "non organic") %>% 
  filter(amendment_code1 != "mixed" ) %>% 
  
  filter(!is.na(yield_av)) %>% 
  filter(!is.na(control_yld_av)) %>% 
  
  ggplot( mapping = aes(control_yld_av, yield_av)) +
  geom_point(aes(colour= amendment_code1),alpha= 0.4) +
  geom_smooth(method = lm, se = FALSE, na.rm = TRUE) +
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~")),
    formula = (y ~ x)
  ) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  theme_bw()+
  theme(legend.position = "none")+
  labs(title = "The data is grouped by site, year and treatment and then average taken\nnote I have also grouped by soil modification and amendment code
    \nFacet wrap is data amendments",
       caption = "note amendment codes: \nnone, non organic and mixed are displayed",
       x = "control yield t/ha", y = "treatment yield t/ha")+
  facet_wrap(.~ amendment_code1)

    





```








```{r subet murray sites, message=FALSE, warning=FALSE, include=FALSE}
unique(ave_site_yr_treat$site)

Murray_sites <- ave_site_yr_treat %>% 
  filter(site == "Bute_CSIRO" | 
           site == "Bute_Trengrove" | 
           site == "Murlong" |
           site == "Younghusband"|
           site == "Ouyen_Spade"|
           site == "Carwarp_Amelioration"
         )
unique(Murray_sites$site)


```

```{r scatter amendment with Murray sites, echo=FALSE, message=FALSE, warning=FALSE}


Murray_sites_plot1 <-  Murray_sites %>% 
  filter(amendment_code1 != "none") %>%  
  filter(amendment_code1 != "non organic") %>% 
  filter(amendment_code1 != "mixed" ) %>% 
  filter(!is.na(yield_av)) %>% 
  filter(!is.na(control_yld_av))





ave_site_yr_treat %>%  
  filter(amendment_code1 != "none") %>%  
  filter(amendment_code1 != "non organic") %>% 
  filter(amendment_code1 != "mixed" ) %>% 
  
  filter(!is.na(yield_av)) %>% 
  filter(!is.na(control_yld_av)) %>% 
  
  ggplot( mapping = aes(control_yld_av, yield_av)) +
  geom_point(alpha= 0.4) +
  #geom_point(aes(colour= amendment_code1),alpha= 0.4) +
  geom_smooth(method = lm, se = FALSE, na.rm = TRUE) +
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~")),
    formula = (y ~ x)
  ) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  theme_bw()+
  theme(legend.position = "right")+
  labs(title = "The data is grouped by site, year and treatment and then average taken\nnote I have also grouped by soil modification and amendment code
    \nFacet wrap is data amendments",
       caption = "note amendment codes: \nnone, non organic and mixed are displayed",
       x = "control yield t/ha", y = "treatment yield t/ha")+
  
  geom_point(data =  Murray_sites_plot1,  aes(control_yld_av, yield_av, colour = site),alpha= 0.4) +
  
  facet_wrap(.~ amendment_code1)

```

## what about when no soil modification was made?

```{r Plot 2 scatter amendment but no soil modification, echo=FALSE, message=FALSE, warning=FALSE}


ave_site_yr_treat %>%  
  filter(amendment_code1 != "none") %>%  
  filter(amendment_code1 != "non organic") %>% 
  filter(amendment_code1 != "mixed" ) %>% 
  
  filter(!is.na(yield_av)) %>% 
  filter(!is.na(control_yld_av)) %>% 
  
  filter(soil_modification == "Unmodified") %>% 
  
  ggplot( mapping = aes(control_yld_av, yield_av,)) +
  geom_point(aes(colour= amendment_code1),alpha= 0.4) +
  geom_smooth(method = lm, se = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~")),
    formula = (y ~ x)
  ) +
  
  theme_bw()+
  theme(legend.position = "none")+
  labs(title = "The data is grouped by site, year and treatment and then average taken.\nBUT no soil modification 
      \nFacet wrap is amendment",
       caption = "note amendment codes: \nnone, non organic and mixed are displayed",
       x = "control yield t/ha", y = "treatment yield t/ha")+
  facet_wrap(.~ amendment_code1)

# ggsave(
#        device = "png",
#        filename = "no soil modification.png",
#        path= "X:/Therese_Jackie/Sandy_soils/Development_database/for_presentations/Jackie/",
#        width=8.62,
#        height = 6.28,
#        dpi=600
# ) 

```



```{r Plot 2 scatter amendment but no soil modification with Murray, echo=FALSE, message=FALSE, warning=FALSE}

Murray_sites_plot2 <-  Murray_sites %>% 
  filter(amendment_code1 != "none") %>%  
  filter(amendment_code1 != "non organic") %>% 
  filter(amendment_code1 != "mixed" ) %>% 
  
  filter(!is.na(yield_av)) %>% 
  filter(!is.na(control_yld_av)) %>% 
  
  filter(soil_modification == "Unmodified") 





ave_site_yr_treat %>%  
  filter(amendment_code1 != "none") %>%  
  filter(amendment_code1 != "non organic") %>% 
  filter(amendment_code1 != "mixed" ) %>% 
  
  filter(!is.na(yield_av)) %>% 
  filter(!is.na(control_yld_av)) %>% 
  
  filter(soil_modification == "Unmodified") %>% 
  
  ggplot( mapping = aes(control_yld_av, yield_av,)) +
  #geom_point(aes(colour= amendment_code1),alpha= 0.4) +
  geom_point(alpha= 0.4) +
  geom_smooth(method = lm, se = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~")),
    formula = (y ~ x)
  ) +
  
  theme_bw()+
  theme(legend.position = "right")+
  labs(title = "The data is grouped by site, year and treatment and then average taken.\nBUT no soil modification 
      \nFacet wrap is amendment",
       caption = "note amendment codes: \nnone, non organic and mixed are displayed",
       x = "control yield t/ha", y = "treatment yield t/ha")+
  
  geom_point(data =  Murray_sites_plot2,  aes(control_yld_av, yield_av, colour = site),alpha= 0.4) +
  
  facet_wrap(.~ amendment_code1)



```


## what about when ANY soil modification was made?

```{r Plot 3 scatter amendment but ANY soil modification, echo=FALSE, message=FALSE, warning=FALSE}

ave_site_yr_treat %>%  
  filter(amendment_code1 != "none") %>%  
  filter(amendment_code1 != "non organic") %>% 
  filter(amendment_code1 != "mixed" ) %>% 
  
  filter(!is.na(yield_av)) %>% 
  filter(!is.na(control_yld_av)) %>% 
  
  filter(soil_modification != "Unmodified") %>% 
  
  
  
  ggplot( mapping = aes(control_yld_av, yield_av,)) +
  geom_point(aes(colour= amendment_code1),alpha= 0.4) +
  geom_smooth(method = lm, se = FALSE) +
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~")),
    formula = (y ~ x)
  ) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  
  theme_bw()+
  theme(legend.position = "none")+
  labs(title = "Ave. ANY soil modification 
      \nFacet wrap is amendment",
       x = "control yield t/ha", y = "treatment yield t/ha")+
  facet_wrap(.~ amendment_code1)


# ggsave(
#        device = "png",
#        filename = "Any amendments soil modification.png",
#        path= "X:/Therese_Jackie/Sandy_soils/Development_database/for_presentations/Jackie/",
#        width=8.62,
#        height = 6.28,
#        dpi=600
# )


```


```{r Plot 3 scatter amendment but ANY soil modification with Murray sites , echo=FALSE, message=FALSE, warning=FALSE}
Murray_sites_plot3 <-  Murray_sites %>% 
  filter(amendment_code1 != "none") %>%  
  filter(amendment_code1 != "non organic") %>% 
  filter(amendment_code1 != "mixed" ) %>% 
  
  filter(!is.na(yield_av)) %>% 
  filter(!is.na(control_yld_av)) %>% 
  
  filter(soil_modification != "Unmodified")

ave_site_yr_treat %>%  
  filter(amendment_code1 != "none") %>%  
  filter(amendment_code1 != "non organic") %>% 
  filter(amendment_code1 != "mixed" ) %>% 
  
  filter(!is.na(yield_av)) %>% 
  filter(!is.na(control_yld_av)) %>% 
  
  filter(soil_modification != "Unmodified") %>% 
  
  
  
  ggplot( mapping = aes(control_yld_av, yield_av,)) +
  geom_point(alpha= 0.4) +
  #geom_point(aes(colour= amendment_code1),alpha= 0.4) +
  geom_smooth(method = lm, se = FALSE) +
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~")),
    formula = (y ~ x)
  ) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  
  theme_bw()+
  theme(legend.position = "right")+
  labs(title = "Ave. ANY soil modification 
      \nFacet wrap is amendment",
       x = "control yield t/ha", y = "treatment yield t/ha")+
  geom_point(data =  Murray_sites_plot3,  aes(control_yld_av, yield_av, colour = site),alpha= 0.4) +
  
  facet_wrap(.~ amendment_code1)


```





